National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: tools to support monitoring decisions

### 2023-09-05 analysis/paper/paper.Rmd
edit to UI paragraph

Integration into caribouMetrics, shiny UI, integration into SpaDES &
SyncroSim.

To make this work more user friendly and accessible to decision makers
we built a user interface that allows for the exploration of different
monitoring and anthropogenic disturbance scenarios. We have also made
the R code and functions needed to carry out this analysis available as
an R package caribouMetrics. We built the user interface as an R Shiny
app [@chang2023], building off and expanding an app published by Eacker
et al. [-@eacker_web-based_2019]. The app allows users to provide
existing local data or simulate data based on national models as shown
above, define an anthropogenic disturbance scenario and make
projections. The results shown are similar to Figure
\@ref(fig:examplePredictions) and allow for comparisons to the national
model. Many parameters controlling the Bayesian model, local data
simulation and antropogenic scenario are exposed in the app with
sensible defaults set, such that novice users can get reasonable results
quickly while advanced user can customise the projections to suite their
needs. The caribouMetrics package is available on GitHub at
<https://github.com/LandSciTech/caribouMetrics> and a package website
with detailed documentation is also available
(<https://landscitech.github.io/caribouMetrics/>).

>>>>

To make this work more user friendly and accessible to decision makers
we built a user interface that allows for the exploration of different
monitoring and anthropogenic disturbance scenarios. We built the user
interface as an R Shiny app [@chang2023], building off and expanding an
app published by Eacker et al. [-@eacker_web-based_2019]. The app allows
users to provide existing local data or simulate data based on national
models as shown above, define an anthropogenic disturbance scenario and
make projections. The results shown are similar to Figure
\@ref(fig:examplePredictions) and allow for comparisons to the national
model. Many parameters controlling the Bayesian model, local data
simulation and antropogenic scenario are exposed in the app with
sensible defaults set, such that novice users can get reasonable results
quickly while advanced user can customise the projections to suite their
needs. We have also made the R code needed to run the app and carry out
the above analysis available as an R package, caribouMetrics. Making our
code available as an R package ensures that it is flexible and can be
re-used or expanded upon in future projects or combined with other tools
and packages (eg SpaDES or SyncroSym). The caribouMetrics package is
available on GitHub at <https://github.com/LandSciTech/caribouMetrics>
and a package website with detailed documentation is also available
(<https://landscitech.github.io/caribouMetrics/>).
